Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-04 ForegroundSimulations/ms.tex
Add paragraph in Delay Spectrum section
From 9e6a4f7 (fgsim):
====================

In ms.tex,

(*) Add paragraph in Delay Spectrum section

>>>>

We note that these visibilities and delay power spectra are dependent on right ascension (RA) of the pointing as well as the center of the frequency band. We defer expressing visibilities and delay power spectra explicitly as a function of pointing or center frequency (or redshift) to later sections where it is necessitated.
